Interpretable Casual Interventions \\ Discourage Spurious Learning

### 2025-04-07 paper/main.tex
overwrite running statistics for causal batchnorm only, reverted SWD to p=2, updated paper to NIPS 2025 style file and added additional benchmarks

% ready for submission
\usepackage{neurips_2024}

@@

\subsection{Benchmark: Hard-Imagenet}
\begin{table}[h!]
	\caption{Accuracies under various ablations, Relative Foreground Sensitivity, on FineTuned ResNet-50 models trained using varying approaches.}
	\centering
	\hspace*{-4em}
	\begin{tabular}{c|c|ccc|c}
		\toprule
		\textbf{Method} & \textbf{None} $(\uparrow)$ & \textbf{Gray Mask FG} $(\downarrow)$ & \textbf{Gray BBOX FG} $(\downarrow)$ & \textbf{Tile FG} $(\downarrow)$ & \textbf{RFS} $(\uparrow)$ \\
		\midrule
		Cross-Entropy & 94.25 & 75.94 & 69.39 & 67.38 & -0.18 \\
		\midrule
		CORM & 92.91 & 76.20 & 69.12 & 68.32 & -0.08 \\
		DFR & \bf 94.39 & 73.53 & 67.51 & 66.71 & -0.27 \\
		CORM + DFR & 91.31 & 72.59 & 63.64 & 63.90 & -0.23 \\
		\midrule
		ACE (Ours) & 89.20 & 47.33 & 34.27 & 34.93 & 0.21 \\
		ACE + SWD (Ours) & 91.20 & \bf 36.13 & \bf 27.20 & \bf 31.60 & \bf 0.28 \\
		ACE + SWD + RevUPs (Ours) & 75.86 & \bf 10.40 & \bf 09.86 & \bf 13.19 & \bf 0.57 \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

% ready for submission
\usepackage{neurips_2025}

@@

\subsection{Benchmark: Hard-Imagenet}
\begin{table}[h!]
	\caption{Accuracies under various ablations, Relative Foreground Sensitivity, on FineTuned ResNet-50 models trained using varying approaches.}
	\centering
	\hspace*{-4em}
	\begin{tabular}{c|c|ccc|c}
		\toprule
		\textbf{Method} & \textbf{None} $(\uparrow)$ & \textbf{Gray Mask FG} $(\downarrow)$ & \textbf{Gray BBOX FG} $(\downarrow)$ & \textbf{Tile FG} $(\downarrow)$ & \textbf{RFS} $(\uparrow)$ \\
		\midrule
		Cross-Entropy & 94.25 & 75.94 & 69.39 & 67.38 & -0.18 \\
		\midrule
		CORM & 92.91 & 76.20 & 69.12 & 68.32 & -0.08 \\
		DFR & \bf 94.39 & 73.53 & 67.51 & 66.71 & -0.27 \\
		CORM + DFR & 91.31 & 72.59 & 63.64 & 63.90 & -0.23 \\
		\midrule
		DyTBN (Baseline) & 93.07 & 76.67 & 71.73 & 68.27 & -0.22 \\
		\midrule
		ACE (Ours) & 89.20 & 47.33 & 34.27 & 34.93 & 0.21 \\
		ACE + SWD (Ours) & 91.20 & \bf 36.13 & \bf 27.20 & \bf 31.60 & \bf 0.28 \\
		ACE + SWD + RevUPs (Ours) & 75.86 & \bf 10.40 & \bf 09.86 & \bf 13.19 & \bf 0.57 \\
		ACE + SWD + DyTBN (Ours) & 87.73 & 45.86 & 34.80 & 40.93 & 0.16 \\
		\midrule
		Gold Standard & 100.00 & 06.67 & 06.67 & 06.67 & 1.00 \\
		\bottomrule
	\end{tabular}
\end{table}
